Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-28 paper.tex
Reorder author list

% to typeset URLs, URIs, and DOIs
\usepackage[english]{babel}
\usepackage{url}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{textcomp}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{amsmath}
\graphicspath{ {./images/} }

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}, Zan-Jun Wang\IEEEauthorrefmark{3}}\\

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{key_certification}
	\caption{Session key certification with blind signature}
	\label{fig:key_certification}
\end{figure}

@@

\subsection{Trading}
Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the subscriber list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers. The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each subscriber. After that, the data provider can also get public keys of each subscriber from the Registration Contact with their accounts. For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature. Consumers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session¸

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{key_exchange}
	\caption{Session key exchange between the data provider and consumer}
	\label{fig:key_exchange}
\end{figure}

\subsection{Refunding}
It is probable that the sensor is malfunctioning after the consumers pay the subscription fee. To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, consumers can ask for refunds. We assume that less than half of consumers in the Product Contract are irrational and malicious. Each subscriber can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th data samples, the subscription fee is proportionally transfered to the data provider, broker and every subscriber. The subscription fee can be prorated as below:

>>>>

% to typeset URLs, URIs, and DOIs
\usepackage[english]{babel}
\usepackage{url}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{textcomp}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{amsmath}

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\

@@

@@

\subsection{Trading}
Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the subscriber list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and subscribers. The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each subscriber. After that, the data provider can also get public keys of each subscriber from the Registration Contact with their accounts. For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext to the Product Contract. Subscribers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature. Subscribers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted sensing data is uploaded to the MAM channel, and subscribers can download and decrypt them with the session¸

\subsection{Refunding}
It is probable that the sensor is malfunctioning after the subscribers pay the subscription fee. To protect subscribers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, subscribers can ask for refunds. We assume that less than half of subscribers in the Product Contract are irrational and malicious. Each subscriber can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th data samples, the subscription fee is proportionally transfered to the data provider, broker and every subscriber. The subscription fee can be prorated as below:
